\documentclass[a4paper,nocourse]{miunasgn}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[swedish,english]{babel}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage[today,nofancy]{svninfo}
\usepackage{listings} 
\usepackage{varioref,prettyref}
\usepackage[natbib,style=numeric-comp,maxbibnames=99,sorting=none,backend=bibtexu]{biblatex}
\addbibresource{literature.bib}
\usepackage[listings,varioref,prettyref]{miunmisc}

\svnInfo $Id$

\courseid{DT145G}
\course{Computer Security}
\assignmenttype{Laboratory Assignment}
\title{Host-Based Intrusion Detection}
\author{Daniel Bosk\footnote{%
  This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 
  Unported license.
	To view a copy of this license, visit 
	\url{http://creativecommons.org/licenses/by-sa/3.0/}.
}}
\date{\svnId}

\begin{document}
\maketitle
\thispagestyle{foot}
\tableofcontents

\section{Introduction}
\label{sec:intro}
This laboratory exercise will cover the topic of intrusion detection
systems (IDS).
An IDS monitors the activity of a system and alert the administrator if any 
potential threats are detected.
This laboratory work will focus on host-based intrusion detection systems 
(HIDS), in particular OSSEC\footnote{%
  URL: \url{http://www.ossec.net/}.
}.


\section{Scope and Aim}
\label{sec:aim}
After completion of this assignment you will
\begin{itemize}
    \input{aims.tex}
\end{itemize}

This laboratory assignment will cover the open source HIDS OSSEC.


\section{Reading instructions}
\label{sec:reading}
\input{literature.tex}


\section{Assignment}
\label{sec:tasks}
This section covers the work to be done and the next section covers how it will 
be examined, and what to be done to pass.

Firstly you should install the OSSEC software.
You can find it on URL
\begin{center}
  \url{http://www.ossec.net/}.
\end{center}
The installation procedure is documented both on the website and in 
\cite{ossec2}, the instructions on the Web are of course more up-to-date.

Once the system is installed and up-and-running, you should select one of the 
features it was designed for, e.g.\ log analysis, real-time alerts, agentless 
monitoring, file integrity checking, active respone, among other things.
You will now evaluate this feature and prepare a demonstration of it.
This demonstration should present at least the following:
\begin{itemize}
  \item What is interesting about this feature?
  \item How you evaluated the feature.
  \item A demonstration of its use.
\end{itemize}


\section{Examination}
\label{sec:examination}
As you will prepare a demonstration, this will be presented for the class 
(check the course schedule for the date of this presentation).
You are required to have some slides to present your selected feature and your 
evaluation, and then of course the live demonstration.
You should give your presentation (demonstration), it should be at most 15 
minutes long.


\printbibliography
\end{document}
